Robust Co-occurrence Quantification for Lexical Distributional Semantics

### 2016-05-31 paper.tex
Layout
Minor

Words that occur in similar context have similar meaning \cite{harris1954distributional}. Thus the meaning of a word can be modeled by counting its co-occurrence with neighboring words in a corpus. Distributional models of meaning represent co-occurrence information in a vector space, where the dimensions are the neighboring words and the values are co-occurrence counts. Successful models need to be able to discriminate co-occurrence information, as not all co-occurrence counts are equally useful, for instance, the co-occurrence with the article \textit{the} is less informative than with a word \textit{existence}. Another fundamental question is the vector space dimensionality and what neighbor words correspond to them.

@@

As context words we select the 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs. All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.~intransitive vs. transitive versions of verbs).

@@

\begin{table}
  \centering
  \begin{tabular}{lll}
    \toprule
    Model           & SimLex-999 & MEN \\
    \midrule
    PPMI$^*$        & 0.393      & 0.745 \\
    SVD$^*$         & 0.432      & 0.778 \\
    SGNS$^*$        & 0.438      & 0.774 \\
    GloVe$^*$       & 0.398      & 0.729 \\
    \addlinespace
    This work       & 0.385      & 0.765 \\
    \bottomrule
  \end{tabular}
  \caption{\textbf{Our model in comparison to the previous work.} On the similarity dataset our model is 0.008 points behind a PPMI model, however on the relatedness dataset 0.020 points above. Note the difference in dimensionality and source corpora, and window size. SVD, SGNS and GloVe numbers are given for comparison. $^*$Results reported by \newcite{TACL570}.}
\label{tab:results}
\end{table}

@@

\section{Acknowledgements}

>>>>

Words that occur in similar context have similar meaning \cite{harris1954distributional}. Thus the meaning of a word can be modeled by counting its co-occurrence with neighboring words in a corpus. Distributional models of meaning represent co-occurrence information in a vector space, where the dimensions are the neighboring words and the values are co-occurrence counts. Successful models need to be able to discriminate co-occurrence information, as not all co-occurrence counts are equally useful, for instance, the co-occurrence with the article \textit{the} is less informative than with the noun \textit{existence}. Another fundamental question is the vector space dimensionality and what neighbor words should correspond to them.

@@

As context words we select the 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs. All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.~intransitive vs.~transitive versions of verbs).

@@

\begin{table}
  \centering
  \begin{tabular}{lll}
    \toprule
    Model           & SimLex-999 & MEN \\
    \midrule
    PPMI$^*$        & 0.393      & 0.745 \\
    SVD$^*$         & 0.432      & 0.778 \\
    SGNS$^*$        & 0.438      & 0.774 \\
    GloVe$^*$       & 0.398      & 0.729 \\
    \addlinespace
    This work       & 0.385      & 0.765 \\
    \bottomrule
  \end{tabular}
  \caption{\textbf{Our model in comparison to the previous work.} On the similarity dataset our model is 0.008 points behind a PPMI model, however on the relatedness dataset 0.020 points above. Note the difference in dimensionality, source corpora and window size. SVD, SGNS and GloVe numbers are given for comparison. $^*$Results reported by \newcite{TACL570}.}
\label{tab:results}
\end{table}

@@

\section*{Acknowledgements}
